---
title: "DATA 607 - Final Project - Food World Cup Recommender System"
author: "Alexander Niculescu, Joshua Bentley, and Kevin Benson"
date: "December xx, 2018"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
        theme: lumen
        number_sections: TRUE
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

what, why, motivation

# Other sections

description of dataset, setup

# Recommender system: food types

recommender system for food world cup

# Exploratory data analysis

some interesting analysis, graphics

# Restaurant suggestions

## Contruct the wrapper function

Once we have the recommended cuisine type and location, the next step is to suggest several restaurants meeting these criteria.  We do this by constructing a wrapper function to access the Yelp Fusion API <https://www.yelp.com/developers/documentation/v3/get_started>.  The wrapper function will return up to 5 restaurants, together with address and other useful information, as provided by the Yelp API.

To start with, we load the `httr` package to access the API and the `jsonlite` package to parse the JSON data returned.  Also, for communicating with the API, we use the API key from a saved environment variable and set up a user-agent string.

```{r message = FALSE}
library(httr)
library(jsonlite)
library(dplyr)
library(stringr)
library(knitr)

# get api key from environment variable
key <- Sys.getenv("yelp_api_key")
api_key <- paste("Bearer", key)
# set user agent for good practice
ua <- user_agent(paste("kecbenson@gmail.com", R.version$platform, R.version$version.string))
```

Next, we define `getRestaurants` as a function of several inputs.  Some brief comments on the code below:

* A. Validate input values for `search` and `where`, and return an error message in case of invalid inputs.  
* B. Next define the query list based on the input values, and send the `GET` request (with the API key in the `Authorization` header) to the API.
* C. Use `fromJSON` to parse the JSON data from the API and return a list object.  Note that we set the `flatten` argument to TRUE, since the dataframe we want has embedded lists in a few columns.
* D. Provide error handling in case the API returns an error.
* E. The dataframe we want is in the `businesses` item in the parsed list, so extract it and then select useful columns to display.  We rename the columns and then return the dataframe.

```{r}
getRestaurants <- function(search = NULL, where = NULL) {
    # A. check valid inputs
    if (!is.character(search) | !is.character(where)) {
        stop("Invalid inputs.\nEnter a cuisine type and location (city, neighborhood, or zip code).")
    }
    
    # B. define url & query list and send GET request 
    url <- "https://api.yelp.com/v3/businesses/search"
    query_list <- list(term = search, 
                       location = where,
                       limit = 5
                       ) 
    resp <- GET(url, add_headers(Authorization = api_key), query = query_list, ua) 

    # C. parse JSON data into list, flatten nested lists
    parsed <- fromJSON(content(resp, as = "text", encoding = "UTF-8" ), flatten = TRUE)

    # D. provide API error handling 
    if (http_error(resp)) {
        stop(
            sprintf(
                "Failed request to Yelp Fusion API\n[%s] %s: %s",
                status_code(resp),
                parsed[[1]]$code,
                parsed[[1]]$description
            ),
            call. = FALSE
        )
    }

    # E. pass businesses list item to dataframe and select & rename columns   
    df <- parsed$businesses %>% select(Name = name, 
                                       Rating = rating,
                                       Reviews = review_count,
                                       Price = price,
                                       Address = location.display_address,
                                       Phone = display_phone,
                                       Website = url
        )
    
    return(df)
}
```

## Test the wrapper function

First let's test the validation of the function arguments.

```{r error = TRUE}
# test input validation
getRestaurants()
getRestaurants(search = NULL, where = "10021")
getRestaurants(search = "steak", where = NA)
```

Next let's test the handling of API error messages.

```{r error = TRUE}
# test API error handling (e.g., no API key)
api_key <- "abc"
getRestaurants("seafood", "10021")
```

Now let's do a sample search and confirm the result is a valid dataframe.

```{r error = TRUE}
# re-set API key
api_key <- paste("Bearer", key)

# search restaurants & confirm result is a valid dataframe
df_test <- getRestaurants("seafood", "10021") 
str(df_test)
kable(df_test, caption = "Seafood in 10021")
```

## Show sample output

Finally let's show some sample output.

``` {r cache = FALSE}
# search steakhouses in brooklyn
getRestaurants("steakhouse", "brooklyn")

# search indian in san diego
getRestaurants("indian", "san diego")
```

# Integrate the recommender system with restaurant suggestions

# Conclusion

## Findings

## Suggestions for further work


